---
title: "p8105_hw1_hms2187_rmarkdown"
author: Henry Stoddard
date: September 13 2020
output: html_document
---
# p8105_hw1_hms2187
# This is my work for hw1
# Question 1

Creating a dataframe using tibble:

```{r df_create}
library(tidyverse)
hw1_df = tibble(
  vec_rand = rnorm(10),
  vec_logic = c(TRUE, TRUE, FALSE, TRUE, FALSE, TRUE, TRUE, FALSE, FALSE, TRUE),
  vec_char = c("here", "are", "some", "words", "I", "hope", "this", "gets", "easier", "haha"),
  vec_factor = factor(c("high", "high", "high", "medium", "medium", "medium", "medium", "low", "low", "low"))
)
summary(hw1_df)
```

Now to look at each variable's mean:
```{r mean}
mean(hw1_df$vec_rand)
mean(hw1_df$vec_logic)
mean(hw1_df$vec_char)
mean(hw1_df$vec_factor)
```

We can get the mean for numeric and logical variables, but not character or factor variables.


Converting to numeric:

```{r conversion, results='hide'}
as.numeric(hw1_df$vec_logic)
as.numeric(hw1_df$vec_char)
as.numeric(hw1_df$vec_factor)
```

Using the as.numeric function, R tries to convert all of the variables into numeric form. So, the logical variable was converted from true/false into 0 or 1. The character variable had NAs introduced by coercion. The factor variable changed its levels from high, medium, low, to 1, 2, and 3. This does explain what happens when we try to take the mean (it shows why mean is NA for these variables).

Now adding additional conversions **left off here**:
```{r conversion2}
vec_logic = hw1_df$vec_logic
hw1_df$vec_logic = as.numeric(hw1_df$vec_logic)