---
title: "p8105_hw1_hms2187_rmarkdown"
author: Henry Stoddard
date: September 13 2020
output: html_document
---
# p8105_hw1_hms2187
This is my work for hw1

```{r tidyverse library}
library(tidyverse)
```

## Problem 1

Creating a dataframe with the specified elements using tibble:

```{r df_create}
hw1_df = tibble(
  vec_rand = rnorm(10),
  vec_logic = vec_rand > 0,
  vec_char = c("here", "are", "some", "words", "I", "hope", "this", "gets", "easier", "haha"),
  vec_factor = factor(c("high", "high", "high", "medium", "medium", "medium", "medium", "low", "low", "low"))
)
summary(hw1_df)
```

Pulling Variables and taking means:
```{r}
mean(pull(hw1_df, vec_rand))
mean(pull(hw1_df, vec_logic))
mean(pull(hw1_df, vec_char))
mean(pull(hw1_df, vec_factor))

```


We can get the mean for numeric and logical variables, but not character or factor variables.


Converting to numeric:

```{r conversion, results='hide'}
as.numeric(pull(hw1_df, vec_rand))
as.numeric(pull(hw1_df, vec_logic))
as.numeric(pull(hw1_df, vec_char))
as.numeric(pull(hw1_df, vec_factor))
```

Using the as.numeric function, R tries to convert all of the variables into numeric form. So, the logical variable was converted from true/false into 0 or 1. The character variable had NAs introduced by coercion. The factor variable changed its levels from high, medium, low, to 1, 2, and 3. This does explain what happens when we try to take the mean (it shows why mean is NA for these variables).

Now adding additional conversions **problem with second bullet point**:
```{r conversion2}
as.numeric(pull(hw1_df, vec_logic)) * pull(hw1_df, vec_rand)

as.factor(pull(hw1_df, vec_logic)) * pull(hw1_df, vec_rand)

vec_logic2 = as.factor(pull(hw1_df, vec_logic))
as.numeric(vec_logic2)*(pull(hw1_df, vec_logic))
```

## Problem 2